Agents and you, a brief summary

### 2015-10-31 agents/summery.tex
Finished another slide.

\subsubsection{Markov process}
A \emph{Markov process} is a stochastic process $X_0, X_1, X_2, \dots$ such 
that:

\[ P\{ X_{n+1} X_n, X_{n-1}, \dots\}=P\{X_{n+1}|X_n\}\]
for $n \ge 0$
\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).

>>>>

\subsection{Markov process}
A \emph{Markov process} is a stochastic process $X_0, X_1, X_2, \dots$ such 
that:

\[ P\{ X_{n+1} X_n, X_{n-1}, \dots\}=P\{X_{n+1}|X_n\}\]
for $n \ge 0$

\subsubsection{Remarks}
If states are numbers, then often state space is denoted by $I$, with 
typical elements $i,j,k$.

A markov process is sometimes called a markov chain. These concepts are
equal.

If $S$ is countably infinite, then the probability transition matrix
can be represented as an ``open ended'' stochastic matrix.
\[
	P =
\begin{pmatrix}
	p_{1,1}	& p_{2,1}	& p_{3,1} & \cdots\\
	p_{1,2}	& p_{2,2}	& p_{3,2}	& \cdots\\
	p_{1,3}	& p_{2,3}	& p_{3,3}	& \cdots\\
	\vdots	& \vdots	& \vdots		& \ddots \\
\end{pmatrix}
\]
With markov proceci it is extremly important to beclear about the
\emph{cardinality of the state space} (finite, discrete, continues) and
the \emph{nature of time} (discrete, continuous)

A \emph{dead state} or a \emph{dead end} is a state that does not have
any outgoing arcs. An \emph{absorbing  state} is a state that has precisely
one outgoing arc with probability 1 to itself.

\subsection{Chapman-Kolmogorov equations}

\[P^{(n)}_{ij} = \sum_{all\mbox{\ }k} P^{(n_1)}_{ik} P^{(n_2)}_{kj} \]

It is convenient to list the $n$-step transition probabilities in a matrix.
\[
	P^{(n)} =
\begin{pmatrix}
	p^{(n)}_{1,1}	& \cdots	& p^{(n)}_{n,3} 	& \\
	\vdots	& \ddots	& \vdots	& \\
	p^{(n)}_{1,n}	& \cdots	& p^{(n)}_{n,n}	& \\
\end{pmatrix}
\]

In particiular $P^{(1)} = P$.

\subsubsection{Lemma}
Suppose $k+l=n$ Where $k,l\ge1$. Then $P^{(k)} \cdot P^{(l)} = P^{(n)}$

(I think this was proven)

$P^{(n)} = P^n$, this was definitivley proven. Not sure why you would
prove removing brackets, but whatever.

\subsection{Classes}
No this aren't default private structures (its a c++ reference).

Classes make dealing with large markov chains easier by grouping nodes
together. \emph{Open classes} allow the process to escape the class once
it enters a \emph{closed class} it will remain there forever.
A class is \emph{Transient} if a process can never reenter it, a
state is recurrent if it can. A process is multichain if there are
multiple recurrent classes, if there is just one reccurent class
its uni-chain.

A critical transition is a transition between classes.

A closed class doesn't have to be recurrent if there are infinite cases.
Otherwise a closed class is always recurrent.
An openclass is always transient.

\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).
